---
title: "HW1 Po-Chun Chen N11957611"
output:
  html_document:
    theme: spacelab
    toc: true
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: true
---


## Chapter 2 
### 2.5 
#### Answer: b,d,e

Let the sample space S represent two coin tosses using a fair coin. Let A be outcomes
in S with at least one head, and let B be an outcome with two heads. Which
of the following are true? </br>
a. S ⊂ A</br>
b. head ∩ head ∈ A</br>
c. head ∩ tail ∉ A</br>
d. S ⊃ B</br>
e. A ⊄ B</br>

Let H denote Head and T denote Tail:</br>
S(Universal Set) = {HH,HT,TH,TT}</br>
A = {HH,HT,TH} at least one head</br>
B = {HH} with two heads</br>

### 2.6
#### Answer: a,b

Which of the following are true?</br>
a. If P(A ∪ B) = P(A), then B ⊂ A</br>
b. If P(A ∩ B) = P(B), then B ⊂ A</br>

$$\begin{equation}\begin{split}P(A \cup B) & = P(A)+P(B)-P(A \cap B)\end{split}\end{equation}$$
$$\because in \,option\,a\, P(A ∪ B) = P(A) $$
$$\therefore P(B) = P(A \cap B)\\B \subset A$$ 
$$\because in \,option\,b\, P(A ∩ B) = P(B) $$
$$\therefore P(A) = P(A \cup B)\\B \subset A$$ 

### 2.13
#### Answer: 32
What are all the possible outcomes (in head and tails) for a toss using five coins.
(see Theorem 2.2)?<br>

$$ Number= 2^5 \\= 32$$
S = {HHHHH, HHHHT, HHHTH, HHTHH, ...TTTTT}

### 2.16

$$Using\, the\, definitions\, of\, r!\, and\, n!\, (Equation 2.23)\, and\, \binom{n}{r}$$
$$ prove \,\binom{n}{r} = \binom{n-1}{r-1}+\binom{n-1}{r}$$

$$\binom{n}{r} = \frac{n!}{r!(n-r)!}$$


$$\begin{equation}\begin{split}\frac{n!}{r!(n-r)!} &= \frac{(n-1)!}{(n-1-(r-1)!(r-1)!} + \frac{(n-1)!}{(n-1-r)!r!} \\&=  \frac{(n-1)!}{(n-r)!(r-1)!} + \frac{(n-1)!}{(n-1-r)!r!}\\&= \frac{(n-1)!}{(n-r)!r!}*r + \frac{(n-1)!}{(n-r)!r!}*(n-r)\end{split}\end{equation}$$
Both side divided by r!(n-r)!

$$ \begin{equation}\begin{split}n! &= (n-1)!*r+(n-1)!*n-r\\&=(n-1)!*(n-r+r)\\&=(n-1)!*n\\&=n!\end{split}\end{equation}$$

### 2.17
#### Answer: 256

DNA contains the nucleotide bases (G, A, T, C). How many different ways can the
bases be rearranged in a 4 base pair strand?

Four spaces with four kinds of nucleotides = $$ 4^4 = 256 $$


## Chapter 3
### 3.1 

|x| −1|0|1|
|--:|:--|:--|:--|
|f(x)|1/8|6/8|1/8|

Let X be a discrete random variable whose pdf is described in the table given here:</br>
Find the following:</br>
a. P(X = 0)</br>
b. P(X < 10)</br>
c. P(0 > X > 0)</br>
d. P(X ≤ 1)</br>
e. F(1)</br>
f. F−1(7/8)</br>
g. R(x), that is, the survivorship function</br>
h. f(x)/R(x), that is, the hazard function</br>

#### a.
$$P(X = 0)=6/8$$

#### b.
$$P(X < 10)=1=P(X =-1)+P(X =1)+P(X =0)=1$$

#### c.
$$P(0 > X > 0)=0\,\\It\, is\,an\,empty\,set$$

#### d.
$$P(X ≤ 1)=1$$

#### e.
$$F(1)=1$$

#### f.
$$ F^{-1}(7/8)=0\geq x\geq-1\, or\, 1\geq x\geq0\ $$

#### g.
$$R(X)=1-F(X)$$

|x| −1|0|1|
|--:|:--|:--|:--|
|f(x)|1/8|6/8|1/8|
|fc(x)|1/8|7/8|1|
|R(x)|7/8|1/8|0|

#### h.

|x| −1|0|1|
|--:|:--|:--|:--|
|f(x)|1/8|6/8|1/8|
|fc(x)|1/8|7/8|1|
|R(x)|7/8|1/8|0|
|f(x)/R(x)|1/7|6|undefined|

### 3.2 

Assume that leaf biomass (in grams) from the plant Salix arctica follows the pdf,</br>
f(x) = 2(x + 1)^-3 for x > 0.</br>
Find the probability of a leaf being between 0 and 3 g, that is, P(0 < X < 3).</br> 
Solve by hand using calculus. Verify your result using R.</br>

$$\int_0 ^3 2(x+1)^{-3} dx = \\ 2*\int_0 ^3 (x+1)^{-3} dx$$
Substitute u=x+1

$$2*\int_0 ^3 u^{-3} dx = \\ -\int_0 ^3 u^{-2} dx =\\ -  (x+1)^{-2}|3,0 +C = 15/16 = 0.9375$$

```{r}
integrand <- function(x) {2*(x+1)^-3}
integrate(integrand, lower = 0, upper = 3)
```


### 3.3

Let X be a continuous random variable with the pdf f(x) = 3x^2 if 0 < x < 1. Find the
following by hand, using calculus if necessary. Verify your results using R.</br>
a. P(X = 0.5), explain your answer</br>
b. P(X < 1), explain your answer</br>
c. P(X ≤ 1), explain your answer</br>
d. P(X > 1), explain your answer</br>
e. P(X < 0.7)</br>
f. P(0.1 < X < 0.6)</br>


#### a.
$$P(X = 0.5)=\int_{1/2}^{1/2} 3x^{2} dx = [x^3]_{1/2}^{1/2}=0$$
Since x is continuous, the probability that x takes on any specific value x is 0

```{r}
integrand <- function(x) {3*(x)^2}
integrate(integrand, lower = 1/2, upper = 1/2)
```

#### b.
$$P(X < 1)=\int_{0}^{1} 3x^{2} dx = [x^3]_{0}^{1}=1$$
```{r}
integrand <- function(x) {3*(x)^2}
integrate(integrand, lower = 0, upper = 1)
```

#### c.
$$P(X \leq 1)=\int_{0}^{1} 3x^{2} dx = [x^3]_{0}^{1}=1$$
The probability of x at 1 is 0
```{r}
integrand <- function(x) {3*(x)^2}
integrate(integrand, lower = 0, upper = 1)
```

#### d.
$$P(X > 1)= 0$$

#### e.
$$P(X < 0.7)= \int_{0}^{0.7} 3x^{2} dx = [x^3]_{0}^{0.7}=0.343$$

```{r}
integrand <- function(x) {3*(x)^2}
integrate(integrand, lower = 0, upper = 0.7)
```

#### f.
$$P(0.1< X < 0.6)= \int_{0}^{0.6} 3x^{2} dx = [x^3]_{0.1}^{0.6}=0.215$$

```{r}
integrand <- function(x) {3*(x)^2}
integrate(integrand, lower = 0.1, upper = 0.6)
```

### 3.4
Let X be a continuous random variable with the pdf f(x) = e^−x, for x > 0. Find the
following by hand, using calculus if necessary. Verify your results using R.</br>
a. P(X < 0), explain your answer</br>
b. P(X > 0), explain your answer</br>
c. P(X < 0.5)</br>
d. P(X ≤ 0.5), explain your answer</br>
e. P(0.1 < X < 1)</br>

#### a.

$$P(X < 0)=\int_{-\infty}^{0} e^{-x} dx =0$$

#### b.

$$P(X > 0)=\int_{0}^{\infty} e^{-x} dx = [-e^{-x}+C]_0^\infty =1$$
Since x>0, the probability of x>0 is 1
```{r}
integrand <- function(x) {exp(-x)}
integrate(integrand, lower = 0, upper = Inf)
```

#### c.

$$P(X <0.5)=\int_{0}^{0.5} e^{-x} dx = [-e^{-x}+C]_0^{0.5} = 1-\frac{1}{\sqrt{e}}$$
```{r}
integrand <- function(x) {exp(-x)}
integrate(integrand, lower = 0, upper = 0.5)
```

#### d.

$$P(X \leq 0.5)=\int_{0}^{0.5} e^{-x} dx = [-e^{-x}+C]_0^{0.5} = 1-\frac{1}{\sqrt{e}}$$
because x is continuous and the probability that x takes on any specific value x is 0

```{r}
integrand <- function(x) {exp(-x)}
integrate(integrand, lower = 0, upper = 0.5)
```

#### d.

$$P(0.1<X<1)=\int_{0.1}^{1} e^{-x} dx = [-e^{-x}+C]_{0.1}^{1} = e^{-1/10}-e^{-1}\simeq0.53$$

```{r}
integrand <- function(x) {exp(-x)}
integrate(integrand, lower = 0.1, upper = 1)
```

### 3.5
You are working on a mark–recapture study of boreal toads, Bufo boreas. </br>
You predict that there is a 40% chance of capturing a marked toad for each of 30 traps that
you establish.</br>
a. What is the probability that exactly 20 marked toads will be found in the 30</br>
traps? Calculate this by hand, and confirm your calculation using R.</br>
b. What is the probability that up to 20 marked toads will be found? Use R.</br>
c. How do these values change if your estimated probability of recapture is 30%,
not 40%?</br>

#### a.

$$P(X=20)=\binom{30}{20}(0.4)^{20}(0.6)^{10}\simeq0.002$$

```{r}
dbinom(20,size = 30,prob = 0.4)
```

#### b.

$$P(X\leq20) = \sum_{x\leq20}f(x) $$
```{r}
sum(dbinom(0:20, 30, 0.4))
```

#### c.
The values become smaller in a but larger in b 

```{r}
dbinom(20,size = 30,prob = 0.3)
sum(dbinom(0:20, 30, 0.3))
```

### 3.8

What is the probability that a predator will capture its third prey item after six independent
attempts given that its probability of capturing prey per attempt is 0.3?</br>

```{r}
choose(6,2)*(0.3)^2*(0.7)^4*0.3
dbinom(2,6,0.3)*0.3
```

### 3.17
Complete the following. Show all code.</br>
a. Create an R object, X, with 10000 random observations from N(0, 1) using
rnorm.</br>
b. Square X, call this object Y.</br>
c. Create an ecdf of Y. Now find the empirical probability P(Y < 1).</br>
d. Assume X ~ χ2(1) and calculate P(X < 1). Comment on your results.</br>

#### a.
```{r results='hide'}
x<-rnorm(10000,0,1)
```

#### b.
```{r}
y<-x^2
```

#### c.
```{r}
ecdf(y)
ecdf(y)(1)
```

#### d.
```{r}
pchisq(1,df=1)
```
two probabilities are almost the same

### 3.18

Assume that the number of sightings for bald eagles (Haliaeetus leucocephalus) at a
site over a 4-week period is Poisson distributed (temporally random) with a mean
λ = 10. What is the probability of having 15 sightings over a 4-week period?

```{r}
dpois(15,10)
```



